\break
\section{Requirements Traceability}
The following table shows how it is the mapping between the goals and their requirements with the design decisions described and analyzed in this document.
\begin{center}
\def\arraystretch{1.5}
\begin{longtable}{|p{0.6\textwidth}|p{0.4\textwidth}|}
	\hline
	Requirements & Design Decisions \\
	\hline\MPtrue
	\begin{itemize}
		\item {[}G1{]} Allow visitors to sign up for the service
	\begin{itemize}
		\item {[}R1{]} The system requests an e-mail or a telephone number during the registration
		\item {[}R2{]} The system rejects an e-mail or a telephone number already used by another registered passenger
		\item {[}R3{]} After the completion of registration process, the system must send a confirmation to newly registered passengers
		\item {[}R4{]} The system checks if e-mails or telephone numbers are well formed
		\item {[}R5{]} The system considers passengers officially registered if and only if passengers either open an activation link in a confirmation e-mail, or insert a code received through a SMS in mobile application or in web service.
	\end{itemize}\end{itemize} & \MPtrue\begin{itemize}
	\item Access control component and interface
	\item Passenger UI Logic component and interface
	\item myTaxiService Database component and interface
	\end{itemize} \\
	\hline\MPtrue
	\begin{itemize}
		\item {[}G2{]} Allow registered passengers to request a taxi
	\begin{itemize}
		\item {[}R1{]} The system must disallow visitors to perform such operation
		\item {[}R2{]} The system has to locate passengers using GPS in his/her smartphone or through browser.
		\item {[}R3{]} After selecting the most appropriate taxi (explained in goal \hyperref[goal4]{[G4]}), the system must inform drivers that a request is incoming.
		\item {[}R4{]} Upon confirmation by the driver about the request of availability, the system has to inform the passenger about a positive outcome,if it occurs, and provide additional information, such as ETA
		\item {[}R5{]} In case of unavailability of a contacted driver, the system has to pick another taxi from the most appropriate queue and to repeat what described in requirement [R3]
		\item {[}R6{]} The system must proceed to the cancellation of the request if and only if the user requested to do it and the condition in [D1] has not met yet.
	\end{itemize}
	\item {[}G3{]} Allow registered passengers to reserve a taxi
	\begin{itemize}
		\item {[}R1{]} The system must disallow visitors to perform such operation.
		\item {[}R2{]} The system must check if time and the date specified is at least past two hours with the respect of present time.
		\item {[}R3{]} The system must disallow the reservation of a taxi with an invalid meeting point.
		\item {[}R4{]} The system must disallow the reservation of a taxi with a meeting point outside the area served by the service.
		\item {[}R5{]} The system shall allocate a timer that will timeouts ten minutes before the time and date specified, triggering the event of allocating a taxi for this reservation.
	\end{itemize}
\end{itemize} & \MPtrue \begin{itemize}
\item Access control component and interface
\item Ride manager component and interface
\item Passenger UI Logic component and interface
\item Maps Service external component and interface
\end{itemize}\\
	\hline\MPtrue
	\begin{itemize}
	\item {[}G4{]} Guarantee a fair management of the taxi queue
	\begin{itemize}
		\item {[}R1{]} The system must select the first free taxi in the queue corresponding to the zone in which the meeting point is.
		\item {[}R2{]} The system has to manage the queue using a predefined policy.
		\item {[}R3{]} If there are no available taxis in a queue, the system scans queues of adjacent zones.
		\item {[}R4{]} The system must remove a taxi from the queue if and only if a passenger has confirmed the intention of taking that taxi.
		\item {[}R5{]} Queues contain only free taxis.
		\item {[}R6{]} The system must not select taxis that belong to drivers who are spending their breaks.
	\end{itemize}
	\end{itemize} & \begin{itemize}\item Queue manager component and interface\end{itemize}\\
	\hline
	\MPtrue
	\begin{itemize}
	\item {[}G5{]} Allow taxi drivers to manage their workday
	\begin{itemize}
	\item {[}R1{]} The system must disallow non-taxi drivers to perform such operations.
	\item {[}R2{]} The system must not allow to start a workday twice or more in the same day.
	\item {[}R3{]} The system must not allow to end a workday before a workday is started.
	\item {[}R4{]} The system must enforce the driver to take some breaks during the day.
	\end{itemize}\end{itemize} &\MPtrue \begin{itemize}
	\item Access control component and interface
	\item Taxi Driver UI Logic component and interface
	\item Queue manager component and interface
\end{itemize} \\
	\hline
	\MPtrue
	\begin{itemize}
	\item {[}G6{]} Allow the system administrator to update the information about drivers and taxis
	\begin{itemize}
		\item {[}R1{]} The system must disallow non-system administrator to perform such operations.
		\item {[}R2{]} The system must disallow the insertion of inconsistent data (for example drivers with invalid license or without a car).
		\item {[}R3{]} The system must disallow the insertion of already present data.
	\end{itemize}\end{itemize} &\MPtrue \begin{itemize}
	\item Access control component and interface
	\item myTaxiService Database component and interface
	\item Cars and Driver external component and database
\end{itemize}\\
\hline
\end{longtable}
\end{center}