\newpage
\section{Introduction}
\subsection{Revision History}
\begin{table}[H]
	\centering
	\begin{tabular*}{\linewidth}{|p{0.1\linewidth}|p{0.13\linewidth}|p{0.3099\linewidth}|p{0.3499\linewidth}|}
		\hline
		\textbf{Version} & \textbf{Date}       & \textbf{Author(s)}         & \textbf{Summary}           \\ \hline
		0.1     & 01/21/2016 & Fioratto Raffaele & Document Creation \\ \hline
	\end{tabular*}
\end{table}
\break
\subsection{Purpose}
\subsection{Scope}
The aim of this project is to create a new brand system that optimizes an 
existing taxi service.
The system will be capable of automatizing and/or simplifying certain 
processes during requests or reservations of taxis.
It will also guarantee a fair management of taxi queues.
New passengers can sign up for services, inserting some basic information in order to use features as soon as possible.
A passenger can request a taxi using web service or mobile
application after registration. The system will be able to localize precisely his/her position, determining taxis that are available near
him/her. The system will select a taxi and then it will forward the request to one of its drivers.
Upon confirmation, the system will notify the customer about the successful completion of the operation and the ETA of the taxi. A passenger can also reserve a taxi by specifying time and date, but he/she has to do it with at least two hours in advance. Cancellation is also permitted. The system will actually process the request ten minutes before the time specified during the reservation in the same way as described previously.
\subsection{Definitions and Abbreviations}
\begin{itemize}
	\item PPD: \textbf{P}roject \textbf{P}lan \textbf{D}ocument
	\item ITP: \textbf{I}ntegration \textbf{T}est \textbf{P}lan
	\item DD: \textbf{D}esign \textbf{D}ocument
	\item RASD: \textbf{R}equirement \textbf{A}nalysis and \textbf{S}pecification \textbf{D}ocument
\end{itemize}
\subsection{Reference Documents}
\begin{itemize}
	\item myTaxiService Project Specification Document
	\item myTaxiService RASD
	\item myTaxiService DD
	\item myTaxiService ITP
	\item \href{http://csse.usc.edu/csse/research/COCOMOII/cocomo2000.0/CII\_modelman2000.0.pdf}{COCOMO II Model Definition Manual}\footnote{Available at: http://csse.usc.edu/csse/research/COCOMOII/cocomo2000.0/CII\_modelman2000.0.pdf}
\end{itemize}